ODGI: scalable tools for pangenome graphs

### 2021-06-01 manuscript/main.tex
added few missing info in the table caption

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
      \processtable{Example of performance improvement between
        \cmd{odgi extract} and \cmd{VG something}. Centromere region
        is extracted from CHR ?? of the HPRC year 1
        assembly\citep{HPRC}, i.e., 88 haploid, phased human genome
        assemblies from 44 individuals plus the chm13 and GRCh38
        reference genomes stored in 100GB(?) GFA format. All timings
        were performed on a server class machine on SSD MODEL with X
        GB of RAM and 48 CPU cores (Y x 12 core AMD Opteron) Processor
        MODEL @ 3.3 GHz with 8MB L2 Cache.\FIXME
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}

>>>>

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
      \processtable{Example of performance improvement between
        \cmd{odgi extract} and \cmd{VG something}. Centromere region
        is extracted from CHR 6 of the HPRC year 1
        assembly\citep{HPRC}, i.e., 88 haploid, phased human genome
        assemblies from 44 individuals plus the chm13 and GRCh38
        reference genomes stored in 4.3GB GFA format. All timings
        were performed on a server class machine on SSD MODEL with X
        GB of RAM and 48 CPU cores (Y x 12 core AMD Opteron) Processor
        MODEL @ 3.3 GHz with 8MB L2 Cache.\FIXME
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}
